### 2017-05-08 frontmatter.tex
First part of first round of corrections

% Declaration
\begin{declaration}
%  \vspace*{1cm}
  I declare that the work in this thesis is mine. Figures and results taken from other sources
include the appropriate reference in the text or figure caption. Figures labelled `CMS' are sourced
directly from CMS publications. The `CMS Preliminary' label indicates figures which
have been made public via a preliminary public document or a public website, but are not
included in a publication in a peer-reviewed journal. Figures labelled `CMS' or `CMS preliminary', 
including those made by myself, include the relevant reference in the figure caption.
The work for the analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} was 
carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
For the results presented in chapter \ref{chap:hhh} I contributed to the data analysis of two out of three
final states presented in the final public result, and I 
was responsible for the statistical inference. This included
the interpretation of the results in MSSM and 2HDM benchmark scenarios. The 
work is included in reference \cite{CMS-HIG-14-034}. For the results presented in chapter~\ref{chap:mssm}
I was responsible for all stages of the analysis, including the optimisation
of object selection and event categorisation, as well as studies of background
methods for three out of four final states in the public result,
evaluation of systematic uncertainties in all four final states, and production of the statistical
results, including model interpretations. This work is included in the most recent
preliminary result \cite{CMS-PAS-HIG-16-037}, as well as a predating preliminary
result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
The work presented in chapter~\ref{sec:mssm_combination} has
not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.

>>>>

% Declaration
\begin{declaration}
  I declare that the work in this thesis is mine. Figures and results taken from other sources
include the appropriate reference in the text or figure caption. Figures labelled `CMS' are sourced
directly from CMS publications. The `CMS Preliminary' label indicates figures which
have been made public via a preliminary public document or a public website, but are not
included in a publication in a peer-reviewed journal. Figures labelled `CMS' or `CMS preliminary', 
including those made by myself, include the relevant reference in the figure caption.
Chapters \ref{chap:theory}--\ref{chap:objects} do not contain original work by myself, however they 
give information on the theoretical background, the CMS detector and the standard reconstruction algorithms
used within the CMS collaboration which underpin my own work described in later chapters.
The work for the \Htohhtobbtautau and \AHtotautau analyses presented in chapters~\ref{chap:hhh} and \ref{chap:mssm} was 
carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
For the results of the \Htohhtobbtautau analysis I contributed to the data analysis of the \etau and \mutau
final states of the di-tau pair. I 
was responsible for the statistical inference of the analyses in the \etau, \mutau and \tautau final states
of the di-tau pair. This included
the interpretation of the results in MSSM and 2HDM benchmark scenarios. The 
work is included in reference \cite{CMS-HIG-14-034}. For the results of the \AHtotautau analysis
I was responsible for all stages of the analysis, including the optimisation
of object selection and event categorisation, as well as studies of background
methods for the \etau, \mutau and \tautau final states in the public result,
evaluation of systematic uncertainties in the \etau, \mutau, \tautau and \emu final states, and production of the statistical
results, including model interpretations. This work is included in the most recent
preliminary result \cite{CMS-PAS-HIG-16-037}, as well as a predating preliminary
result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
The work on the combination of \AHtotautau analyses presented in chapter~\ref{sec:mssm_combination} has
not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.
\enlargethispage{2\baselineskip}
